Test

### 2020-07-05 non_publication/original_bookdown_files/04-results.Rmd
Moved files to archive folder

cof_bio %>%
  kable("html", align = 'clc', caption = 'Biophysical Model') %>%
    kable_styling(full_width = F, position = "float_left")

cof_full %>%
  kable("html", align = 'clc', caption = 'Full Model') %>%
    kable_styling(full_width = F, position = "right")
```

>>>>

cof_bio %>%
  kable("latex", align = 'clc', caption = 'Biophysical Model') %>%
    kable_styling(full_width = F, position = "float_left")

cof_full %>%
  kable("latex", align = 'clc', caption = 'Full Model') %>%
    kable_styling(full_width = F, position = "right")
```
